MS_CNuptake.Rmd

### 2022-08-30 MS_CNuptake.Rmd
update

# Setup 
```{r setup, include=FALSE}
library(MLmetrics)
library(vhs) ##remotes::install_github("cj-holmes/vhs")
library(tidyverse) 
library(ncmeta)
library(viridis)
library(ggthemes)
library(LSD)
library(yardstick)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gplots)
library(tidyselect)
library(extrafont)
library(caret)
library(recipes)
devtools::load_all("/Users/yunpeng/yunkepeng/rbeni_new/rbeni/") # using beni's latest package.
#library(rbeni)
library(raster)
library(maps)
library(rworldmap)
library(cowplot)
library(ncdf4)
library(scales)
library(lme4)
library(lmerTest)
library("PerformanceAnalytics")
library(MuMIn)
library(tidyverse)
library(ggplot2)
library(lme4)
library(visreg)
library(ggpubr)
library(car)
library("ggplotify")
library(remotes)
library(tune)
library(relaimpo)

@@

#ggsave(paste("./output/newphy_figs3.jpg",sep=""), width = 20, height = 20)
```

>>>>

# Setup 
```{r setup, include=FALSE}
library(MLmetrics)
library(vhs) ##remotes::install_github("cj-holmes/vhs")
library(tidyverse) 
library(ncmeta)
library(viridis)
library(ggthemes)
library(LSD)
library(yardstick)
library(ggplot2)
library(RColorBrewer)
library(dplyr)
library(gplots)
library(tidyselect)
library(extrafont)
library(caret)
library(recipes)
devtools::load_all("/Users/yunpeng/yunkepeng/latest_packages/rbeni/") # using beni's latest package.
#library(rbeni)
library(raster)
library(maps)
library(rworldmap)
library(cowplot)
library(ncdf4)
library(scales)
library(lme4)
library(lmerTest)
library("PerformanceAnalytics")
library(MuMIn)
library(tidyverse)
library(ggplot2)
library(lme4)
library(visreg)
library(ggpubr)
library(car)
library("ggplotify")
library(remotes)
library(tune)
library(relaimpo)

@@

#ggsave(paste("./output/newphy_figs3.jpg",sep=""), width = 20, height = 20)

plot_grid(a1,a2,a3,a4,a5,
          a6,a7,a8,a9,white,nrow=2)+white

ggsave(paste("./output/newphy_figs3a.jpg",sep=""), width = 20, height = 20*0.4)

plot_grid(a10,a11,a12,white,white,
          a13,a14,white,white,white,nrow=2)+white

ggsave(paste("./output/newphy_figs3b.jpg",sep=""), width = 20, height = 20*0.4)

plot_grid(a15,a16,white,white,white,nrow=1)+white

ggsave(paste("./output/newphy_figs3c.jpg",sep=""), width = 20, height = 20*0.2)
